Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-08 paper/paper.Rmd
para fix

author-note:
    "*These authors contributed equally and are listed alphabetically. **Carolyn Au, Juan Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampinen, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan. Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."

abstract: 
    "Replications are important to science, but who will do them? One proposal is that students can conduct direct replications as part of their training. As a proof-of-concept for this idea, here we report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course. This work provides an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt. Congruent with previous findings, replication studies typically yielded smaller effects than originals: The modal outcome was partial support for the original claim. We describe the workflow and pedagogical methods that were used in the class and discuss challenges for adoption of this pedagogical model and replication research more broadly."

@@

In the current article, we provide evidence on this issue by reporting the results of replication projects conducted in a single class (a graduate-level experimental methods course). As part of the required work of the course, students conducted high-power, direct replications of published articles from the 2015 volume of the journal *Psychological Science*. These studies both give evidence about the state of replicability in the field and provide insight into the process of pedagogical replication.

It is a challenging proposition to estimate the replicability of an entire literature [cf. @osc2015]. Making such an estimate minimally requires determining a sampling strategy, a notion of what constitutes a direct replication, and a standard for what constitutes a successful replication, among many other difficult decisions [@gilbert2016;@anderson2016]. In the current work, we focus on a quantity that is easier to estimate: the probability that a graduate student can choose an article of interest in *Psychological Science* and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the basic pattern of findings with sufficient fidelity to be able to build on it in future work. We believe that this notion of whether a piece of research supports cumulative progress is an important construct. Whether an independent scientist can build on a published result is perhaps as important as whether the work is replicable in a more conceptual sense -- and in many cases easier to determine.

@@

In sum, we view the contribution of the current work to be two-fold. First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom. Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced -- supporting the same theoretical claims -- by a motivated student.

@@

All projects were completed as part of a graduate-level methodology class (syllabus and materials available at [http://psych254.stanford.edu]()). At the initiation of class, all students were told that they had the opportunity to contribute their individual class assignment to a group replication project. The requirements for joining the project were to conduct a pre-registered replication of a finding from the 2015 volume of *Psychological Science* and to contribute the code, data, and materials to the writeup.

>>>>

author-note:
    "*These authors contributed equally and are listed alphabetically. **Carolyn Au, Juan Miguel Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampinen, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan. Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."

abstract: 
    "Replications are important to science, but who will do them? One proposal is that students can conduct direct replications as part of their training. As a proof-of-concept for this idea, here we report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course. This work provides an estimate of the probability that a motivated graduate student can reproduce a previously published result on a first attempt. Congruent with previous studies, replications typically yielded smaller effects than originals: The modal outcome was partial support for the original claim. We describe the workflow and pedagogical methods that were used in the class and discuss challenges both for the adoption of this pedagogical model and for replication research more broadly."

@@

In the current article, we report the results of replication projects conducted in a single class (a graduate-level experimental methods course). As part of the required work of the course, students conducted high-power, direct replications of published articles from the 2015 volume of the journal *Psychological Science*. These studies both give evidence about the state of replicability in the field and provide insight into the challenges and promise of pedagogical replication.

Past work has attempted to estimate the proportion of true effects in a particular literature [@ioannidis2005;@osc2015], but this goal is challenging -- perhaps even impossible [@gilbert2016;@anderson2016]. Assessing the truth of even an individual effect relies on delineating what constitutes an exact replication [@cites] and establishing a standard for replication success [@simonsohn2015]. Estimating the proportion of true effects in a literature further requires a systematic sampling strategy to ensure generality. Furthermore, no single replication attempt is definitive, so multiple iterations are typically necessary to increase the evidential value of replication attempts [@lewis2016;@klein2014].

In the current work, we do not address these challenges directly; instead, our goal is more modest. We assess the probability that a graduate student can choose an article of interest in the 2015 volume of *Psychological Science* and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the findings. We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations. While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work.

@@

In sum, we view the contribution of the current work to be two-fold. First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom. Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced by a motivated student.

@@

All projects were completed as part of a graduate-level methodology class (syllabus and materials available at [http://http://web.stanford.edu/class/psych254/2016/]()). At the initiation of class, all students were told that they had the opportunity to contribute their individual class assignment to a group replication project. The requirements for joining the project were to conduct a pre-registered replication of a finding from the 2015 volume of *Psychological Science* and to contribute the code, data, and materials to the writeup.
